---
title: "p8105_hw1_zz2900.Rmd"
author: "Zhenyu Zhou"
date: "2022-09-22"
output: html_document
---
```{r}
library(tidyverse)
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1
Use the following code (in your RMarkdown file) to load the penguins dataset:

```{r penguins}
#load the penguins dataset
data("penguins", package = "palmerpenguins")
penguins

```
Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code. In your discussion, please include:

* the data in this dataset, including names / values of important variables:

  * There are 8 important variables in the penguins dataset. These 8 variables are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, year.

* the size of the dataset (using nrow and ncol):
  * The row number of penguins is `r nrow(penguins)` and column number of penguins is `r ncol(penguins)`. So the size of the dataset is `r nrow(penguins) * ncol(penguins)`.

* the mean flipper length:
```{r}
#drop NA from penguins data frame
noNA_penguins = drop_na(penguins)

#get the mean of fliiper length
flipperMean = mean(pull(noNA_penguins, flipper_length_mm))
flipperMean
```

Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable (adding color = ... inside of aes in your ggplot code should help).

Export your first scatterplot to your project directory using ggsave.

```{r}
## scatterplot of flipper_length_mm (y) vs bill_length_mm (x)
ggplot(noNA_penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot.pdf")
```

